\section{Integrals over submanifolds}

Let's remind ourselves why we are doing all of this. Among the "final bosses" of Analysis 2 is for instance the Divergence Theorem, stating
\begin{align*}
	\int_{\Omega} \sum_{i=1}^{n} \partial_{i}F_{i} \, dx = \int_{\partial \Omega} F \cdot \nu \, dS,
\end{align*}
for $\Omega \subset \mathbb{R}^{n}$ open, $\partial \Omega$ a $C^{1}$ submanifold and $F \in C^{1}(\overline{ \Omega }, \mathbb{R}^{n})$. Now, we already know a big portion of this expression. We know open sets, boundaries, submanifolds, partial derivatives and integrals over sets with respect to the Jordan measure. The last part missing is what it means to take the integral over the submanifold $\partial \Omega$ with the surface measure $dS$.

So that's what we're working on now. First, we need to define volumes of parametrised $d$-dimensional submanifolds. We start with the easiest case, i.e. $1$-dimensional manifolds. We will call them lines and their volume lengths.

% \begin{remark}[$C^{k}$ function on non-open domains]
% 	If $A \subset \mathbb{R}^n$ is not open we say that $f \in C^k\left(A, \mathbb{R}^n\right)$ if there exist $U \supset A$ open and $\widetilde{f} \in C^k\left(U, \mathbb{R}^n\right)$ such that $\widetilde{f}=f$ when restricted to $A$.
% \end{remark}

\begin{definition}[Parametrised $1$-manifold (curve)]\label{def:curve-new}
	We call $M \subset \mathbb{R}^{n}$ a curve if it is a $1$-dimensional submanifold. Usually, we attribute to $M$ a parametrisation (in the sense of \ref{prop:char-manifold} (4), but $G$ is global) $\phi: V \to \mathbb{R}^{n}$ with $V \subset \mathbb{R}$ open such that $M \subset \phi(V)$, which we also call a curve.
\end{definition}

\begin{definition}[Length of a curve]\label{def:length}
	Let $V \subset \mathbb{R}$ open, such that $[a,b] \subset V$ and $\phi: V \to \mathbb{R}^{n}$ a curve. Then we define the length of the curve from $a$ to $b$ as
	\begin{align*}
		L(\phi([a,b])) = \int_{a}^{b} \left| \phi'(t) \right| \, dt.
	\end{align*}
	% nice picture of a curve, with the part [a,b] highlighted
\end{definition}

What do we imagine this length of a curve should satisfy?
\begin{enumerate}
	\item Independence of a reparametrisation $\phi \to \phi \circ \psi$,
	\item Additivity,
	\item Invariance under Euclidean isometry,
	\item Normalisation, so the length of $[0,1] \times \left\{ 0 \right\} \in \mathbb{R} \times \mathbb{R}^{n-1}$ should be $1$.
\end{enumerate}
Now, for 1, we will prove a general variant soon, 2 follows the additivity of the one-dimensional integral. A Euclidean isometry is a map of the form $F(x) = Rx + b$, where $R$ is an orthogonal $n \times n$ matrix. But then
\begin{align*}
	(F \circ \phi)'(t) = D(F \circ \phi)(t) = DF(\phi(t)) \cdot D\phi(t) = R \cdot \phi'(t),
\end{align*}
and in particular since $\lVert R \rVert_{2} = 1$ (Linear Algebra), we get $\left| (F \circ \phi)'(t) \right| = \left| \phi'(t) \right|$. Normalisation can be verified by computation.

Now this we can extend to general dimensions. Notation-wise, when I say $M$ is \textit{parametrised by} $\phi$, I'm referring to the characterisation of a submanifold from Proposition \ref{prop:char-manifold} (4) and assuming that the parametrisation $\phi$ suffices for all points on $M$ (we will later hopefully introduce partitions of unity which take care of this). When I asked the professor about this ambiguity, he argued this is just how it is in differential geometry. So henceforth a curve can be either, and it will have to be clear from the context. The same 

\begin{definition}[$d$-Volume of parametrised $d$-submanifold]\label{def:d-vol}
	Let $V \subset \mathbb{R}^{d}$ open and $M \subset \mathbb{R}^{n}$ a $d$-dimensional manifold parametrised by $\phi: V \to \mathbb{R}^{n}$. Let $E \subset V$ Jordan measurable with $\overline{ E } \subset V$, then we define the $d$-volume of $\phi(E)$ as
	\begin{align*}
		\text{vol}_{d}(\phi(E)) = \int_{E} \sqrt{ \det (D \phi^\top D \phi)}(x) \, dx.
	\end{align*}
	We call the quantity $\sqrt{\det (D\phi^\top D \phi)}$ the \textit{Gram Determinant} and it is a continuous function $\overline{ E }  \to \mathbb{R}$, hence the integral is well-defined by \ref{lem:unif-cont-func-int}.
\end{definition}

\begin{remark}[Gram determinant]
	Let $L$ be an $n \times d$ matrix with $d \leq n$ and rank $d$. Then $L^\top L$ is a $d \times d$ matrix of full rank (see Linalg 2 exercise sheet 8) and $\sqrt{\det (L^\top L)}$ is the Gram determinant. To check that the square root exists, consider that $L^\top L$ is diagonalisable and its eigenvalues are all positive (see proof of \ref{lem:polar-decomp}).

	For $d = 2$, one checks as an exercise that if $L = (v,w)$ for $v,w \in \mathbb{R}^{3}$, then
	\begin{align*}
		\det (L^\top L) = \left| v \times w \right|^{2} = \left| v \right|^{2} \left| w \right|^{2} - (v \cdot w)^{2}.
	\end{align*}
	In particular, if $\phi: V \to \mathbb{R}^{3}$ is a parametrisation of the surface $M$, then for $E \subset V$ Jordan measurable such that $\overline{ E } \subset V$,
	\begin{align*}
		A(\phi(E)) := \text{vol}_{2}(\phi(E)) = \int_{E} \left| \partial_{1} \phi \times \partial_{2} \phi \right|.
	\end{align*}
	See also slides from the interactive presentation by Serra, I think it provides a very different and much more intuitive understanding on why this is a \textit{good} definition for $d$-volume.
\end{remark}

\begin{eg} [Area of the sphere]
	We parametrise the unit ball $B_{1}(0) \subset \mathbb{R}^{3}$ with
	\begin{align*}
		\Psi(\theta, \varphi) =
		\begin{pmatrix}
			\cos\varphi \cos \theta  \\
			\sin \varphi \cos \theta \\
			\sin\theta
		\end{pmatrix}.
	\end{align*}
	Then the area (so $2$-volume) of $B_{1}$ is given by (ignore sets of measure $0$ as always)
	\begin{align*}
		A\Big(\Psi\Big((0,2\pi) \times (-\tfrac{\pi}{2}, \tfrac{\pi}{2})\Big)\Big) = \int_{0}^{2\pi} \int_{-\pi / 2}^{\pi / 2} \sqrt{\det D \Psi^\top D \Psi}  \, d\varphi d\theta.
	\end{align*}
	One computes
	\begin{align*}
		D \Psi^\top D \Psi =
		\begin{pmatrix}
			1 & 0 \\ 0 & \cos^{2}\theta
		\end{pmatrix} \implies \det (D \Phi^\top D \Phi) = \cos^{2} \theta,
	\end{align*}
	which we can bring back to compute
	\begin{align*}
		A (B_{1}) = \int_{0}^{2\pi} \int_{-\pi / 2}^{ \pi / 2} \cos\theta  \, d\theta  d\varphi = 4 \pi.
	\end{align*}
\end{eg}

\begin{lemma}[Invariance under reparametrisation]\label{lem:invar-repar}
	Let $V, W \subset \mathbb{R}^{d}$ open and $M \subset \mathbb{R}^{n}$ a $d$-dimensional manifold parametrised by $\phi: V \to \mathbb{R}^{n}$. Assume that $\psi: W \to V$ is a $C^{1}$ diffeomorphism and let $E \subset V$ Jordan measurable such that $\overline{ E } \subset V$. Then
	\begin{align*}
		\text{vol}_{d}(\phi(E)) = \text{vol}_{d}(\phi \circ \psi( \psi^{-1}(E) )).
	\end{align*}
\end{lemma}
\begin{proof}
	We compute
	\begin{align*}
		D(\phi \circ \psi)(x) = D\phi(\psi(x)) \cdot D\psi(x) \implies D(\phi \circ \psi)(x)^\top = D\psi(x)^\top \cdot D \phi(\psi(x))^\top.
	\end{align*}
	This we use to find the Gram determinant
	\begin{align*}
		\det (D(\phi \circ \psi)^\top D(\phi \circ \psi)) = \det (D \psi^\top D(\phi \circ \psi)^\top D(\phi \circ \psi) D\psi) = \det (D \psi)^{2} \cdot \det (D\phi D\phi^\top) \circ \psi.
	\end{align*}
	We integrate over this using change of variables \ref{thm:change-of-vars}
	\begin{align*}
		\int_{E} \sqrt{\det (D \phi^{T} D \phi)}(x) \, dx = \int_{\psi^{-1}(E)} \sqrt{\det (D\phi^\top D\phi)}(\psi(x)) \left| \det D \psi(y) \right| \, dy
	\end{align*}
	and plug in the Gram determinant we computed to get
	\begin{align*}
		\int_{\psi^{-1}(E)} \sqrt{ \det (D \psi)^{2}\det (D\phi D\phi^\top) \circ \psi }(y)  \, dy.
	\end{align*}
	But then the respective definitions of the $d$-volumes match.
\end{proof}

\begin{remark}[The issue with reparametrisation]
	Assume we are given multiple parametrisations for parts of a manifold that might intersect. In particular, assume we have some manifold $M$ and that we have $\phi_{i}: V_{i} \to M \cap W_{i}$ for $i = 1,2$. It is possible that $\widetilde{M} := M \cap (W_{1} \cap W_{2}) \neq \emptyset$. In general, the $d$-volume of $\phi$ and $\psi$ will not be the same, because they don't even look at the same parts of a manifold. What really matters is that they align on the part of the manifold where they intersect.

	We check this by redefining the parametrisation $\phi_{i}: \widetilde{V}_{i} \to \widetilde{M}$ with $\widetilde{V}_{i} = \phi_{i}^{-1}(\widetilde{M})$. Then we define $\psi = \phi_{2}^{-1} \circ \phi_{1}: \widetilde{V}_{1} \to \widetilde{V}_{2}$, which is of class $C^{1}$ (check notes). And so it remains to show the $d$-volume is invariant under the reparametrisation with this $\psi$, which we know is true by \ref{lem:invar-repar}.
\end{remark}

\begin{lemma}[Invariance under orthogonal transformations]\label{lem:inv-ortho-trans}
	Let $V \subset \mathbb{R}^{d}$ open and $M \subset \mathbb{R}^{n}$ a $d$-dimensional manifold parametrised by $\phi: V \to \mathbb{R}^{n}$. Let $R \in O(n)$. Then for $E \subset V$ Jordan measurable such that $\overline{ E } \subset V$,
	\begin{align*}
		\text{vol}_{d}(R \phi(E)) = \text{vol}_{d}(\phi(E)).
	\end{align*}
\end{lemma}
\begin{proof}
	Use the fact that for any linear map $L: \mathbb{R}^{d} \to \mathbb{R}^{n}$, we gave \begin{align*}
		\det ((RL)^\top RL) = \det (L^\top R^\top R L) = \det (L^\top L).
	\end{align*}
	The rest is obvious.
\end{proof}

\begin{remark}[More intuition about the Gram determinant]
	Let $L$ be an $n \times d$ matrix of rank $d$. We know $L( \mathbb{R}^{d})$ is a $d$-dimensional subspace. By Linear Algebra, there exists $R \in O(n)$ such that $RL = \begin{pmatrix} \widetilde{L} \\ 0 \end{pmatrix}$ for $\widetilde{L}$ a $d \times d$ matrix. But then,
	\begin{align*}
		\sqrt{\det ((RL)^\top RL)} = \sqrt{\det (\widetilde{L}^\top \widetilde{L})} = \left| \det (\widetilde{L}) \right| = \left| \det (\widetilde{L}[0,1]^{d}) \right| = \left| \det (L[0,1]^{d}) \right|,
	\end{align*}
	so the Gram determinant gives us precisely the stretching of $d$-dimensional volume. So like $L([0,1]^{d})$ would be some parallelepiped in $\mathbb{R}^{n}$, $\widetilde{L}([0,1]^{d})$ would be the projection of that onto a flat subspace, where $\det \widetilde{L}$ tells us exactly how the $d$-volume is stretched.
\end{remark}

\begin{definition}[Support of a function]\label{def:support-func}
	Let $U \subset \mathbb{R}^{n}$ be open and $f: U \to \mathbb{R}$ continuous. Define the support of $f$ as
	\begin{align*}
		\text{spt}(f) = \overline{ \left\{ x \in U \mid f(x) \neq 0 \right\} }.
	\end{align*}
	If $\text{spt}(f)$ is bounded, we call $f$ compactly supported in $U$.
\end{definition}

\begin{definition}[Integral over submanifold]\label{def:int-subm}
	Let $V \subset \mathbb{R}^{d}$ open, $M \subset \mathbb{R}^{n}$ a $d$-dimensional submanifold parametrised by $\phi: V \to \mathbb{R}^{n}$ such that $\phi(V) = M$ and $f: \phi(V) \to \mathbb{R}^{n}$ continuous such that $\text{spt}(f \circ \phi) \subset V$. Then
	\begin{align*}
		\int_{M} f(p) \, d \text{vol}_{M}(p) = \int_{M} f \, d \text{vol}_{M} := \int_{V} \Big((f \circ \phi) \cdot \sqrt{\det (D\phi^\top D\phi)}\Big)(x) \, dx.
	\end{align*}
\end{definition}

\begin{remark}[Integral is well-defined]
	The integral exists because $V$ is open and the support $\text{spt}(f)$ is covered by finitely many balls $B_{r_{i}}(x_{i}) \subset V$ such that $A := \bigcup_{i = 1}^{N} B_{r_{i} / 2}(x_{i}) \subset V$ and $\overline{ A } \subset V$. But since $f$ is zero on $V \setminus \overline{ A } $, it suffices to take the integral not over $V$, but over $\overline{ A } $, so we know it exists by \ref{lem:unif-cont-func-int}.	
\end{remark}
